### 2020-01-08 Article.tex

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}

@@

We define the set of free variables of a formula as usual. 
We will use the notation $\phi(\overbar{y})$ to refer to a 
formula $\phi\in FO[\sigma]$
to denote that its free variables are the ones in $\overbar{y}$.
Formulas with no free variables are called sentences. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
formula, $\overbar{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overbar{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.

@@

For the rest of the article consider fixed:
\begin{itemize}
	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$.\

@@

We define the class $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ as the 
class of $\sigma$-structures that
satisfy the 
following axioms: 
\begin{itemize}
	\item \textit{Symmetry axioms}: For each $1\leq s \leq t$ and
	each $g\in \Phi_s$:
	\[ \forall x_1,\dots, x_{a_s} \big(  R_s(x_1,\dots, x_{a_s})
	\iff R_s(x_{g(1)},\dots,x_{g(a_s)}) \big)    \]
	\item \textit{Anti-reflexivity axioms}: For each 
	$1\leq s \leq t$ and $\{i,j\}\in P_s$
	\[ \forall x_1,\dots, x_{a_s} 
	\big( (x_i=x_j) \implies \neg R_s(x_1,\dots, x_{a_s})
	\big)\]
	\end{itemize}

@@

\begin{definition} 
Let $V$ be a set. A \textbf{ multi-hypergraph with
vertex set $V$, $t$ edge sets, with edge sizes given by $\overbar{a}$,
symmetry groups $\overbar{\Phi}$, and anti-reflexivity restrictions $\overbar{P}$}
is a pair $G=(V,\overbar{E})$, where $\overbar{E}=E_1,\dots, E_t$ and
for each $i$, $E_i \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
\end{definition}

For the sake of word economy the expression ``multi-hypergraph with
vertex set $V$, $t$ edge sets, with edge sizes given by $\overbar{a}$,
symmetry groups $\overbar{\Phi}$, and anti-reflexivity restrictions $\overbar{P}$" 
will be replaced simply by ``hypergraph". The word ``hypergraph" will not hold
any other meaning than this for the rest of this writing except for the places
where it is explicitly stated.  \par

Hypergraphs, as we have defined them, can be naturally interpreted as
structures from $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ in the following way: 
given $G=(V,\overbar{E})$,
we consider $V$ to be the universe of $G$, and for any $i$ we define
$R_i^G\subseteq V^{a_i}$ as the set such that
$(\overbar{x})\in V^{a_i}$, $(\overbar{x})\in R_i^G$ if and only if 
$[\overbar{x}]\in E_i$. Under this interpretation hypergraphs, by definition,
satisfy the symmetry and anti-reflexivity axioms given above. It is also easy to
see that this interpretation induces a one-to-one identification between 
structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ and hypergraphs. \par

@@

Let $\overbar{p}:=p_1\dots,p_t$.
The random model $G^{\mathcal{C}}(n,\overbar{p})$ 
is the discrete probability space that
assigns to each hypergraph $G$ whose vertex
set $V(G)$ is $[n]$ the following probability:

\[ \mathrm{Pr}(G)=\prod_{i=1}^{t} p_i^{|E_i(G)|}
(1-p_i)^{ |E^{[n]}_{a_i,\Phi_i,P_i}|-|E_i(G)|}.	
\]
Equivalently, this is the probability space obtained by 
assigning to each edge with color $i$,  
$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability $p_i$ independently.

@@

@@

In the three cases, if $\overbar{v}$ and $\overbar{v}$
are lists in $\mathcal{X}[s-1]$ and $\mathcal{Y}[s-1]$
respectively that share the same mark and remain unmodified
in $\mathcal{X}[s]$ and $\mathcal{Y}[s]$, then by the 
induction hypothesis $\overbar{v}$ and $\overbar{v}$
have $(k-s+1)$-similar $r_{k-s+1}$-neighborhoods. This
easily implies that they also have
$(k-s)$-similar $r_{k-s}$-neighborhoods.\par
At the end of the game, if $\overbar{v}\in \mathcal{X}[k]$ and 
$\overbar{u}\in \mathcal{Y}[k]$ are lists with the same mark
then the natural mapping between $\overbar{v}$ and $\overbar{u}$
defines an isomorphism between $G_1[\overbar{v}]$ and $G_2[\overbar{u}]$.

We show now an outline of the proof. \par 
We show that for any quantifier rank $k$ there are some classes of graphs 
$C^k_1,\dots, C^k_{n_k}$ such that
\begin{itemize}[noitemsep, topsep=0pt]
	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
	\item[(2)] a.a.s. any random graph belongs to some of them, and
	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
\end{itemize}

After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
$G$ a random graph in $G(n,\beta/n)$. \par

The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
allow ourselves to just sketch some of the proofs during this chapter.

@@

\end{proof}

>>>>

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}

@@

We define the set of free variables of a formula as usual. 
We will use the notation $\phi(\overbar{y})$ to refer to a 
formula $\phi\in FO[\sigma]$
to denote that its free variables are the ones in $\overbar{y}$.
Formulas with no free variables are called sentences. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
formula, $\overbar{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overbar{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}

@@

For the rest of the article consider fixed:
\begin{itemize}
	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$, with 
	all the $a_i$'s greater than $1$.\

@@

We will only consider relational structures where the relations
are of arity at least two. This restriction is not necessary, but 
it makes notation easier. 
\todo[inline]{Quiz\'as deber\'ia a\~nadir un anexo dando alguna indicaci\'on sobre c\'omo tratar las relaciones unarias?}

%We will denote by $t_u$ the, possibly zero,
%amount of unary
%relation symbols in $\sigma$. 
%For the sake of convenience we may assume that $R_i$'s are
%ordered in such a way that the unary relation symbols, if any, 
%are the first ones $R_1,\dots, R_{t_u}$. This will
%become relevant later. \par

We define the class $\mathcal{C}$ as the 
class of $\sigma$-structures that
satisfy the 
following axioms: 
\begin{itemize}
	\item \textit{Symmetry axioms}: For each $1\leq s \leq t$ and
	each $g\in \Phi_s$:
	\[ \forall x_1,\dots, x_{a_s} \big(  R_s(x_1,\dots, x_{a_s})
	\iff R_s(x_{g(1)},\dots,x_{g(a_s)}) \big)    \]
	\item \textit{Anti-reflexivity axioms}: For each 
	$1\leq s \leq t$ and $\{i,j\}\in P_s$
	\[ \forall x_1,\dots, x_{a_s} 
	\big( (x_i=x_j) \implies \neg R_s(x_1,\dots, x_{a_s})
	\big)\]
	\end{itemize}

@@

\begin{definition} 
A \textbf{ multi-hypergraph with
with $t$ edge sets, edge sizes given by
$\overbar{a}$,
symmetry groups $\overbar{\Phi}$, 
and anti-reflexivity restrictions $\overbar{P}$}
is a pair $G=(V(G),\overbar{E(G)})$,
where $\overbar{E(G)}=E_1(G),\dots, E_t(G)$ and
for each $i$, $E_i(G) \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
\end{definition}

For the sake of word economy the expression 
``multi-hypergraph with
$t$ edge sets, with edge sizes given by $\overbar{a}$,
symmetry groups $\overbar{\Phi}$, and anti-reflexivity 
restrictions $\overbar{P}$" 
will be replaced simply by ``hypergraph ". The word 
``hypergraph" will not hold
any other meaning than this for the rest 
of this writing except for the places
where it is explicitly stated.  \par

Hypergraphs, as we have defined them, 
can be naturally interpreted as
structures from $\mathcal{C}^
{\sigma}_{\overbar{\Phi},\overbar{P}}$ 
in the following way: 
given $G=(V,\overbar{E})$,
we consider $V$ to be the universe of
 $G$, and for any $i$ we define
$R_i^G\subseteq V^{a_i}$ as the set such that
$(\overbar{x})\in V^{a_i}$, 
$(\overbar{x})\in R_i^G$ if and only if 
$[\overbar{x}]\in E_i$. Under 
this interpretation hypergraphs, by definition,
satisfy the symmetry and anti-reflexivity
axioms given above. It is also easy to
see that this interpretation induces
a one-to-one identification between 
structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi}
,\overbar{P}}$ and hypergraphs. \par

We will use standard nomenclature and notation
from graph theory. This way, we will call vertex set
to $V(G)$ and vertices to its elements. Likewise, each of 
the $E_i(G)$'s will be called an edge set and its elements, 
edges. Given an edge set $E_i(G)$, the index $i$ will
be called its color, and the number
$a_i$ its size. Thus, we will say that
an edge $e\in E_i(G)$ has color $i$ and size
$a_i$.

Given a set of vertices $U\subseteq V(G)$, 
we will denote by $G[U]$ the hypergraph induced
by $G$ on $U$. That is, $G[U]$ is an hypergraph
$H=(V(H),\overbar{E(H)})$ such that $V(H)=U$ and
for any list $\overbar{v}$ of vertices in $U$,
$[\overbar{v}]\in E_i(H)$ if and only if 
$[\overbar{v}]\in E_i(G)$.
\par

An homomorphism between two hypergraphs $G$ and $H$ 
a map $f:V(G)\rightarrow V(H)$ that sends edges 
from $G$ to edges in $H$ of the same color. That is,
if vertices $v_1,\dots, v_{a_i}$ form an edge 
$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
If $f$ is injective then it is called a monomorphism. 
If $f$ is bijective and its inverse is also an homomorphism 
between $H$ and $G$ then $f$ is called an isomorphism.\par

The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
of isomorphisms between $G$ and itself. 
\par

Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is

The excess $ex(G)$ of an hypergraph $G$ is the number
\[
ex(G)= \big(\sum_{i=1}^{t} (a_i-1)|E_i(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. Here the "weighted number of edges"
in $G$ the sum of the weight of all its edges, where the
weight of an edge is its size minus one.

@@

Let $p_1\dots,p_t$ real numbers between zero and one,
and let $\overbar{p}=p_1,\dots,p_t$.
The random model $G^{\mathcal{C}}(n,\overbar{p})$ 
is the discrete probability space that
assigns to each hypergraph $G$ whose vertex
set $V(G)$ is $[n]$ the following probability:

\[ \mathrm{Pr}(G)=\prod_{i=1}^{t} p_i^{|E_i(G)|}
(1-p_i)^{ |E^{[n]}_{a_i,\Phi_i,P_i}|-|E_i(G)|}.	
\]
Equivalently, this is the probability space obtained by 
assigning to each edge with color $i$,  
$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability 
$p_i$ independently. \par

%Let $G_n$ denote a random hypergraph in 
%$G^\mathcal{C}(n,\overbar{p})$, where 
%$\bar{p}:=p_1,\dots,p_t$, and 
%we allow each $p_i$ to depend on $n$. 
As in the case of Lynch's theorem, we are interested in the
"sparse regime" of $G^\mathcal{C}(n,\overbar{p})$, were the 
expected number of edges each color is linear. 
%In other words, we want that
%$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
This is achieved when each of the $p_i$'s are 
of the form $\beta_i/n^{a_i-1}$ for some 
non-negative real numbers $\beta_1,\dots,\beta_t$.
Let $\overbar{\beta}:=\beta_1,\dots,\beta_t$.
We will write $\overbar{p}(n,\overbar{\beta})$ to denote 
the list $\beta_1/n^{a_1-1},\dots, \beta_t/n^{a_t-1}$.
We will treat
the parameters $\beta_1,\dots, \beta_t$ as fixed
real constants for the most part and will abbreviate 
$\overbar{p}(n,\overbar{\beta})$ as $\overbar{p}(n)$.\par

Our goal is to prove the following theorem:
%is to prove that for any sentence $\phi\in FO[\sigma]$,
%the limit 
%\[\Ln \mathrm{Pr}(G^\mathcal{C}(n,\overbar{p}
%(n,\overbar{\beta})) \models \phi)\] 
%is well defined and varies 
%analytically with $\overbar{\beta}$.
% Some care is needed
%in order to formulate this precisely, as there are some values
%of $\overbar{\beta}$ for which $\overbar{p}
%(n,\overbar{\beta})$ asymptotically does not 
%define a list of 
%proper probabilities. 
%Indeed, suppose that some relation
%symbol $R_i$ in $\sigma$ is unary. 
%Then, by definition $a_i=1$ and
%the expression $\beta_i/n^{a_i-1}$ 
%equals $\beta_i$. 
%In consequence, if we assign 
%values to $\overbar{\beta}$ and let
%$\beta_i>1$ then the random 
%model $G^\mathcal{C}(n,\overbar{p}
%(n,\overbar{\beta})$ will not be well defined. 
%To avoid this we need to impose $\beta_i\in [0,1]$ 
%for all the $i$'s such that $a_i=1$. \par
%For the sake of convenience we will adopt the convention
%that the unary relation symbols among $R_1,\dots,R_t$ 
%are the first ones, and we will denote by $t_u$ the 
%(possibly zero) number of such relations. 
%Thus $a_1= a_2 =\dots= a_{t_0}=1$, and $a_i>1$ 
%for $i>t_0$. Now we are in conditions of stating our main 
%theorem:

\begin{theorem} \label{thm:main}
	Let $\phi$ be a sentence in $FO[\sigma]$. Then
	the function
	%$F_\phi: [0,1]^{t_u}\times [0,\infty)^{t-t_u}
	$F_\phi: [0,\infty)^{t}
	\rightarrow \R$ given by 
	\[
	\overbar{\beta} \mapsto \Ln Pr\big( G^\mathcal{C}(n,\overbar{p}
	(n,\overbar{\beta})) \models \phi\big)
	\]
	is well defined and analytic. 
\end{theorem}

@@

We show now an outline of the proof. \par 
We show that for any quantifier rank $k$ there are some classes of
hypergraphs 
$C^k_1,\dots, C^k_{n_k}$ such that
\begin{itemize}[noitemsep, topsep=0pt]
	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
	\item[(2)] a.a.s. any random graph belongs to some of them, and
	\item[(3)] the limit probability of random graph belonging to any of them is an analytic expression on the parameters $\overbar{\beta}$. 
\end{itemize}

After this is archived the theorem follows easily.

The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).

\todo[inline]{Explicar esto mejor}

@@

	In the three cases, if $\overbar{v}$ and $\overbar{v}$
	are lists in $\mathcal{X}[s-1]$ and $\mathcal{Y}[s-1]$
	respectively that share the same mark and remain unmodified
	in $\mathcal{X}[s]$ and $\mathcal{Y}[s]$, then by the 
	induction hypothesis $\overbar{v}$ and $\overbar{v}$
	have $(k-s+1)$-similar $r_{k-s+1}$-neighborhoods. This
	easily implies that they also have
	$(k-s)$-similar $r_{k-s}$-neighborhoods.\par
	At the end of the game, if $\overbar{v}\in \mathcal{X}[k]$ and 
	$\overbar{u}\in \mathcal{Y}[k]$ are lists with the same mark
	then the natural mapping between $\overbar{v}$ and $\overbar{u}$
	defines an isomorphism between $G_1[\overbar{v}]$ and $G_2[\overbar{u}]$.
\end{proof}

\todo[inline]{Quiz\'as reordenando esta demostraci\'on se puede acortar o se entiende mejor.}

\subsection{Types of trees}

We define tree $T$ as a connected hypergraph such that
$ex(T)=-1$. We define a vertex-rooted tree $(T,v)$ 
as a tree $T$ with a 
distinguished vertex $v\in V(T)$ called its root. We will
usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. We define the set
of initial edges of a vertex-rooted tree $(T,v)$ as the
set of edges in $T$ that contain $v$. \par
%
%Similarly, we define an edge-rooted tree $(T,e,v)$
%as a tree $T$ with a distinguished edge $e\in E(T)$ and
%a distinguished vertex $v\in e$. \par
Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
we define $Tree_{(T,v)}(u)$ as the tree $T[X]$ induced on the
set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
$, to which we assign $u$ as the root.
That is, $Tree_{(T,v)}(u)$ is the tree consisting of those vertices
whose only path to $v$ contains $u$.
\par
We define the radius of a vertex-rooted, or edge-rooted,
tree as the maximum distance between its marked
vertex and any other one. \par

Fix a natural number $k$. We will define 
two equivalence relations, one between 
rooted trees and another between pairs
$(T,e)$ of rooted trees $T$ and initial edges
$e\in E(T)$. We will name both relations
$k$-equivalence relations and
denote them by $\morph{k}$. 
They are defined recursively as follows:

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent 
	.Notice that those trees
	consist only of one vertex, their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$.
	\begin{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with radius
		at most $r+1$, and let $e_1, e_2$
		be initial edges of $T_1$ and $T_2$ respectively.
		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
		$e_1$ and $e_2$ have the same color and there is a bijection 
		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
		$e_2$ such that:
		\begin{itemize}
			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
			\item If $v_1$ and $v_2$ are the roots of
			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
			\item For any vertex different from the root $u\in e_1$, it is satisfied that
			\[Tree_{(T_1,v_1)}(u)\morph{k} Tree_{(T_2,v_2)}(f(u)).\]
		\end{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with
		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
		$e\in E(T)$, the "quantity 
		of initial edges $e_1$ from $T_1$ that satisfy
		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
		of initial edges $e_2$ from $T_2$ that satisfy
		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
		are both greater than $k-1$.

	\end{itemize}
\end{itemize}

We want prove the following
\begin{theorem} \label{thm:equivalenttrees} 
	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees.
	Then, if they are $k$-equivalent Duplicator wins
	$d\ehr_{k}(T_1,v_1,T_2,v_2)$.
\end{theorem}

Before proceeding with the proof that we need an auxiliary
result. Let $(T,v)$ be a rooted tree and $e$ an 
initial edge of $T$. We define $Tree_{(T_v)}(e)$ as
the induced tree $T[X]$ on the set
$X:=\{v\} \cup \{\, u\in V(T) \, | \, d(v,u) = |e| + d(e,v) \,\}$,
to which we assign $v$ as the root. In other words, 
$Tree_{(T_v)}(e)$ is the tree formed of $v$ and all the vertices
in $T$ whose only path to $v$ contain $e$. 
Now we can check the following:

\begin{lemma} \label{lem:equivalentedges}
	Fix $r>0$. Suppose that theorem \ref{thm:equivalenttrees}
	holds for rooted trees with radii at most $r$.
	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees with radii
	at most $r+1$. Let $e_1$ and $e_2$ be initial edges 
	of $T_1$ and $T_2$ respectively satisfying 
	$(T_1,e_1)\simeq_k (T_2,e_2)$. Name 
	$T^\prime_1=Tree_{(T_1,v_1)}(e_1)$ and 
	$T^\prime_2=Tree_{(T_2,v_2)}(e_2)$. Then
	Duplicator wins $d\ehr{k}(T^\prime_1, v_1, T^\prime_2,v_2)$.
\end{lemma}
\begin{proof}
	We show a winning strategy for Duplicator. 
	Suppose that in the $i$-th round of the game Spoiler
	plays on $T^\prime_1$. The other case is symmetric. Let
	$f:e_1\rightarrow e_2$ be a bijection as in the definition
	of $(T_1,e_1)\simeq_k (T_2,e_2)$. There are two possibilities:
	\begin{itemize}
		\item If Spoiler plays a vertex $v$ on $e_1$ 
		then Duplicator can play $f(v)$ on $e_2$. 
		\item Otherwise, Spoiler plays a vertex $v$ that belongs
		to some $Tree_{(T^\prime_1,v_1)}(u)$ for a unique $u\in e_1$
		different from the root $v_1$.
		By the definition of $(T_1,e_1)\simeq_k (T_2,e_2)$,
		$Tree_{(T^\prime_1,v_1)}(u)\simeq_k 
		Tree_{(T^\prime_2,v_2)}(f(u))$. As both these trees
		have radii at most $r$, by assumption Duplicator has a winning 
		strategy between them and they can follow it.		
	\end{itemize}
\end{proof}

Now we can prove the main theorem of this section:

\begin{proof}[Proof of \cref{thm:equivalenttrees}]~ \par
	Notice that, as $T_1\morph{k} T_2$, both $T_1$ and
	$T_2$ have the same radius $r$.
	We prove the result by induction on $r$.
	If $r=0$ then both $T_1$ and $T_2$ consist
	of only one vertex and we are done. \par
	Now let $r>0$ and assume that the 
	statement is true for all lesser values of $r$.
	We will show that there is a winning strategy 
	for Duplicator in
	$d\ehr_k(T_1,v_1,T_2,v_2)$.
	At the start of the game, set all the initial edges
	in $T_1$ and $T_2$ as non-marked. 
	Suppose that in the $i$-th round Spoiler plays in 
	$T_1$. The other case is symmetric. 
	\begin{itemize}
		\item If Spoiler plays $v_1$ then Duplicator plays $v_2$.
		\item Otherwise, the vertex played by Spoiler belongs to
		$Tree_{(T_1,v_1)}(e_1)$
		for a unique initial edge $e_1$ of $T_1$. 
		There are two possibilities:
		\begin{itemize}
			\item If $e_1$ is not marked yet, mark it with
			the index $i$. In this case, there is a 
			non-marked initial
			edge $e_2$ in $T_2$ satisfying 
			$(T_1,e_1)\simeq_k (T_2,e_2)$.
			Mark $e_2$ with the index $i$ as well. 
			Because of
			\cref{lem:equivalentedges}, Duplicator
			has a winning strategy in
			\[d\ehr{k}(Tree_{T_1}(e_1), v_1, 
			Tree_{T_1}(e_2),v_2)\] and can play according to it.
			\item If $e_1$ is already marked then there is
			a unique initial edge $e_2$ in $T_2$ marked with 
			the same mark as $e_1$ and 	
			$(T_1,e_1)\simeq_k (T_2,e_2)$. Again, 
			Because of
			\cref{lem:equivalentedges}, Duplicator
			has a winning strategy in
			\[d\ehr{k}(Tree_{T_1}(e_1), v_1, 
			Tree_{T_1}(e_2),v_2)\] and can
			continue playing 
			according to it.

		\end{itemize}
		Then Duplicator can find an initial 
		edge $e_2$ of $T_2$ such that
		$(T_1,e_1)\simeq_k (T_2,e_2)$.
		Because of
		\cref{lem:equivalentedges}, Duplicator
		has a winning strategy in
		$d\ehr{k}(Tree_{T_1}(e_1), v_1, 
		Tree_{T_1}(e_2),v_2) $ and can play according to it.
	\end{itemize}

\end{proof}
\todo[inline]{probablemente con alg\'un dibujo sencillo esta demostraci\'on se entienda mejor}

\subsection{Probabilistic results}

Given a natural numbers $n$ and $l$ we will use 
$(n)_l$ to denote 
$n(n-1)\cdots (n-l+1)$ or $1$ if $l=0$.

Our main tool for computing probabilities will be
the following multivariate version of Brun's Sieve 
CITA REQUERIDA

\begin{theorem}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{1,n},\dots, X_{k,n}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} (X_{i,n})_{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{1,n},\dots,X_{k,n}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

\subsection{Almost all hypergraphs are simple}

We say that a connected hypergraph $G$ is \textbf{dense} if
$ex(G)>0$.
We want to show that a.a.s any sub-hypergraph 
of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ whose
diameter is small (i.e. bounded by some constant)
is not dense. \par
It takes a direct computation to show that given
an hypergraph $H$, the number of different (not necessarily
induced) sub-hypergraphs of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$
isomorphic to $H$ belongs to $\Theta(n^{-ex(H)})$.
Indeed, let $N:=|V(H)|$ and let $\phi$ be the automorphism
group of $H$. Then, each sequence $v_1,\dots,v_N$ of $N$
different vertices in $[n]$ can either define a copy of $H$
in $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ or not. Also, each
sequence

\subsection{Probabilities of trees}

In this section we want to show that, given various classes of
$k$-equivalence over rooted trees of radii at most $r$,
$\mathcal{T}_1,\dots,\mathcal{T}_l$, and for 
any fixed vertices $v_1,\dots,v_l \in \N$,
the limit probabilities that each $N(v_i;r)$ is a tree which
belongs to $\mathcal{T}_i$ class when rooted at $v_i$ are
independent and they vary analitically with $\overbar{\beta}$.\par

%
%expressions analytic in $\overbar{\beta}$
%
%\begin{lemma}
%	Let $v_1,\dots,v_l \in [n]$	
%	
%\end{lemma}

@@
